---
title: "Playing with Data Viz R"
author: "Jia Xin"
date: "23 January 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## R Markdown

Playing with Data visualisation for school stuff. 
just for fun. 


```{r cars}

data(mtcars)
df <- as.data.frame(mtcars)
df$cyl <- as.factor(df$cyl)
df$gear <- as.factor(df$gear)
df$am <- as.factor(df$am)
#summary(df)
str(df)

counts <- table(mtcars$am, mtcars$gear)

barplot(counts, main="car distribution by gears and trasnmisssion", xlab="no of gears", ylab = "numbers", col=c("darkblue","red"), legend.text = rownames(counts), names.arg = colnames(counts))

plot(mtcars$mpg, mtcars$hp, xlab = "mpg", ylab = "hp", main = "mpg vs. hp",
     col = "red", cex = 5*abs(mtcars$disp)/max(abs(mtcars$disp)) )

#cex is to control the size of the dot. you pass in a small forumla (try a few times)
text(mtcars$mpg, mtcars$hp, row.names(mtcars), cex=0.6, pos=1, col="blue")

#for the coplot 
coplot(mpg~hp|gear, data=df, row=1)
# qPlot
qplot(x = hp, y = mpg, data = df, color = cyl, facets = .~ gear)

qplot(x = hp, y = mpg, data = df, color = cyl,
facets= .~ gear, shape = am, label = rownames(mtcars),
geom=c("text","point"), size=.5, hjust=-0.1)


```

## Including Plots

You can also plot 3d plots like the ones below; 

```{r pressure, echo=FALSE}

library(scatterplot3d)
attach(mtcars)
scatterplot3d(mpg, wt, disp, main="3D Scatterplot")


library(rgl)
plot3d(wt, disp, mpg, col="red", size=3)

```

other types of chart such as Chernoff face , parallel plot etcs 

e.g. width of the face are those with higher cylinder cars 
similiar characteristics (i.e same face or twins) indicate similiar car performance e.g Cadillac and Lincoln. 

cfvx  vrrrrrr 
```{r pressure1, echo=FALSE}
#install.packages("aplpack")
library(aplpack)
faces(mtcars)

library(lattice)
parallelplot(~mtcars | am,
mtcars)


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r car}

## PCA 
library(mds)

d <- dist(df)
fit <- cmdscale(d,eig=TRUE, k=2)

fit

x <- fit$points[,1]
y <- fit$points[,2]
plot(x, y, xlab="Coordinate 1", ylab="Coordinate 2", main="Metric MDS", type="n")
text(x, y, labels = row.names(df), cex=.6, pos=4, col="blue")